Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/extensions.tex
intro to labeled object shit

@@

Thus, an extension that allows supports such fine-grained explicitly
labeled values is essential.
%
To this end, we extend the IFC calculus with explicitly labeled
values, much like those of LIO and
Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |tv ::= cdots
inlinesep Lb il tv|.
%
Following LIO, we say that the value |tv| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
Directly, the label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |tv|, it
must first raise it label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
When creating labeled values the label |il| must be above
the current label; otherwise it cannot be said that protection has
been transferred from the current label to |il|.
%
(For these rules, we assume that the |Lb| constructor is not part of
the surface syntax and thus cannot be accessed directly to construct
or destruct such values without label checks.)
% 
We omit the reduction rules for labeled values since they closely
follow those presented in~\cite{lio}.
%
Here, we lastly remark that that---albeit in a straight forward
way---the TSNI proof must account for this new construct, since it
appears in the IFC calculus.
%}

\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}

>>>>

Different concrete IFC implementations may wish to extend our minimal
system with labeled constructs appropriate for their envisioned
applications.
%
For example, SWAPI provides a labeled version of the XHR object, while
LIO implements a labeled file system, use in severer-side web
applications~\cite{hails}.
%
However, since proving non-interference for a concrete implementation
follows by isomorphism to the specification language, below we
consider the addition of several labeled constructs to the latter.
%
We remark that that the non-interference proofs must account for the
new constructs, since they amend the IFC calculus semantics (usually
by addition).

@@

Thus, an extension that allows supports such fine-grained explicitly
labeled values is essential.
%
To this end, we extend the IFC calculus with explicitly labeled
values, much like those of LIO and
Breeze~\cite{lio, Hritcu:2013:YIB:2497621.2498098}: |tv ::= cdots
inlinesep Lb il tv|.
%
Following LIO, we say that the value |tv| is protected by label |il|,
while the label |il| itself is protected by the task's current label.
%
%
Directly, the label of such values can be inspected the task without
requiring the current label to be raised.
%
However, when a task wishes to inspect the protected value |tv|, it
must first raise it label to at least |il| to reflect that it is
incorporating data at such sensitivity level in its scope.
%
When creating labeled values the label |il| must be above
the current label; otherwise it cannot be said that protection has
been transferred from the current label to |il|.
%
(For these rules, we assume that the |Lb| constructor is not part of
the surface syntax and thus cannot be accessed directly to construct
or destruct such values without label checks.)
% 
We omit the reduction rules for labeled values since they closely
follow those presented in~\cite{lio}.
%}

\paragraph{Labeled mutable references/variables/channels}
%
In a similar manner, extending the
